---
title: "Extra Exp O-MINDS S"
author: "Hyuna Cho"
date: "20/07/2021"
output: html_document
---

This experiment examined whether using the software would make memorability more consistent between groups, increasing effect size.

Participants (N=95) were presented with

# Load data
```{r Load packages}

rm(list = ls()) # clear environment

library(data.table) # Version 1.12.8

data_dir = "~/data/" # relative to where the script is located

```

```{r Load data}

relevantData = list.files(path = data_dir, full.names = TRUE)

data = data.table()
for (i in relevantData) {
  df_temp = setDT(read.csv(i))
  df_temp[, filename := i]
  data = rbind(data, df_temp)
}

data = setDT(data)

```

# Clean data

```{r Denote batches and remove unnecessary columns}

data$group = NULL #remove group col

#identify batches 
data[grep(pattern = "extraexperiment_1_", x = filename, ), batch := 1 ]
data[grep(pattern = "extraexperiment_2_", x = filename, ), batch := 2 ]
data[grep(pattern = "extraexperiment_3_", x = filename, ), batch := 3 ]
data[grep(pattern = "extraexperiment_4_", x = filename, ), batch := 4 ]
data[grep(pattern = "extraexperiment_5_", x = filename, ), batch := 5 ]
data[grep(pattern = "extraexperiment_6_", x = filename, ), batch := 6 ]
data[grep(pattern = "extraexperiment_7_", x = filename, ), batch := 7 ]
data[grep(pattern = "extraexperiment_8_", x = filename, ), batch := 8 ]
data[grep(pattern = "extraexperiment_9_", x = filename, ), batch := 9 ]
data[grep(pattern = "extraexperiment_10_", x = filename, ), batch := 10 ]
data[grep(pattern = "extraexperiment_11_", x = filename, ), batch := 11 ]
data[grep(pattern = "extraexperiment_12_", x = filename, ), batch := 12 ]
data[grep(pattern = "extraexperiment_13_", x = filename, ), batch := 13 ]
data[grep(pattern = "extraexperiment_14_", x = filename, ), batch := 14 ]
data[grep(pattern = "extraexperiment_15_", x = filename, ), batch := 15 ]
data[grep(pattern = "extraexperiment_16_", x = filename, ), batch := 16 ]

to_assign_ids = data[, .N, keyby = .(batch, subject)]  
to_assign_ids[, participant := 1:.N] #add new participant column
to_assign_ids$N = NULL

data = left_join(data, to_assign_ids)

data = data %>% arrange(participant) %>% select(participant, everything()) # arrange by participant

# remove unnecessary columns

data$filename = NULL

# rename key presses for retrieval phase to be interpretable
data[blockcode == "retrieval" & response == "36", response := "old"]
data[blockcode == "retrieval" & response == "37", response := "new"]


```

## Retrieval data cleaning

Trials were eliminated if the response occurred before 300ms, or if they failed to respond by the end of the trial (2000ms).

Participants were eliminated (N=17) if more than half of their trials (post-cleaning) were of abnormal latency, or if more than half th trials were not seen. This left 38 participants in the RANDOM group and 40 participants in the SOFTWARE group.

```{r Retrieval data cleaning}

retrieval = data[blockcode == "retrieval" & latency %between% c(300,1999)]

exclude_incomplete_retrieval = retrieval[, .N, by = .(participant)][N < 160]$participant #more than half their trials were of abnormal latency or they didn't finish

retrieval = retrieval[!participant %in% c(exclude_incomplete_retrieval)]

# label conditions
retrieval$condition = "random"
retrieval[batch %in% c(9:16)]$condition = "software"

```

```{r Save retrieval data for later analyses}

# remove unnecessary columns
retrieval$subject = NULL
retrieval$blockcode = NULL
retrieval$trialcode = NULL
retrieval$group = NULL
retrieval$encoding_condition = NULL

# label conditions
retrieval$condition = "random" # batches 1-8
retrieval[batch %in% c(9:16)]$condition = "software" # batches 9-16

# create csv
write.csv(retrieval, file = "Extra_retrieval.csv")

```
