---
title: "Nameability_Clean_Object_Project"
author: "Sarah"
date: "11/06/2020"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---
# Load in Data

```{r load packages}

rm(list = ls()) #run this line to clear your environment
library(tidyverse); library(data.table); library(dtplyr); library(hausekeep); library(tidyr); library(hunspell)

data_dir = "/Users/sarahberger/Desktop/ObjectProject/nameability/"

```

Load relevant data and save csv filename to a new column
```{r load data}
relevantData = list.files(path = data_dir, full.names = TRUE)

data = data.table() #create empty datatable
for (i in relevantData) {
  print(i)
  df_temp = tbl_dt(read.csv(i)) #save each iteration of csv file to df_temp
  df_temp[, filename := i] #create new column in df_temp called filename, reflecting name of file
  data = rbind(data, df_temp) #bind filename to data 
}

data = tbl_dt(data)

```

New columns for condition and batch
```{r new columns to denote condition and batch}

data$group = NULL #remove group col

#identify batches 
data[grep(pattern = "batch_1", x = filename, ), batch := 1 ]
data[grep(pattern = "batch_2", x = filename, ), batch := 2 ]
data[grep(pattern = "batch_3", x = filename, ), batch := 3 ]
data[grep(pattern = "batch_4", x = filename, ), batch := 4 ]
data[grep(pattern = "batch_5", x = filename, ), batch := 5 ]
data[grep(pattern = "batch_6", x = filename, ), batch := 6 ]
data[grep(pattern = "batch_7", x = filename, ), batch := 7 ]
data[grep(pattern = "batch_8", x = filename, ), batch := 8 ]
data[grep(pattern = "batch_9", x = filename, ), batch := 9 ]

```

Create new subject IDs
```{r create new participant IDs}

data[, n_distinct(subject, batch)] #number of participants

to_assign_ids = data[, .N, keyby = .(subject, batch)] #save new object
to_assign_ids[, participant := 1:.N] #add new participant column
to_assign_ids$N = NULL

data = left_join(data, to_assign_ids)

data_full = copy(data)

```


```{r clean data table}
  
data = subset(data, select= c(participant, batch, blocknum, trialnum, stimulusitem2, response, latency))

data = data[blocknum == "2"]
data$blocknum = NULL
```


```{r get rid of enter name}

gsub("Enter Name", "", data$response)

data[grep(pattern = "Enter Name", x = response), response_grep := data$response]

write.csv(data, "nameability.csv")

data_clean = read.csv("/Users/sarahberger/Desktop/ObjectProject/old_nameability.csv") #reupload after scoring
```

## Organize the data table by stimulus
```{r organize table by stimulus} 

data_clean=tbl_dt(data_clean) #should have done trimws() here

amount = data_clean[, .N, by = stimulusitem2] #how many stimulus presentations for each? Extra batch has double the presentations

data_by_stimulus = data_clean[, .(lower_response, participant, latency, batch), by = stimulusitem2]

data_by_stimulus = data_by_stimulus[, stimulus_presentations := .N, by = stimulusitem2]

unique_responses = data_by_stimulus[, .(unique(c(lower_response)), .N), by = .(stimulusitem2, lower_response, stimulus_presentations, batch)]%>%arrange(stimulusitem2)

unique_responses$V1 = NULL

```

# Calculate stimulus statistics

```{r calculate h-index}

unique_responses[, proportion_response := N/stimulus_presentations]

unique_responses[, h_index := proportion_response*log2(1/proportion_response)]

unique_responses[, h_index_sum := sum(h_index), by = stimulusitem2]

stimulus_by_h_index = unique_responses[, .(unique(stimulusitem2)), by = h_index_sum]%>%arrange(desc(h_index_sum))

names(stimulus_by_h_index)[2] = "stimulusitem2"

```


```{r compute modal name}

unique_responses = unique_responses%>%arrange(desc(N))

stimulus_mode = unique_responses[, .SD[1], by = stimulusitem2 ]

nameability_dt = left_join(stimulus_by_h_index, stimulus_mode)

nameability_dt = nameability_dt[, .(stimulusitem2, h_index_sum, lower_response, proportion_response)]

names(nameability_dt)
names(nameability_dt)[1] = "stimulus"
names(nameability_dt)[2] = "h_index"
names(nameability_dt)[3] = "modal_response"

nameability_dt[modal_response == "", modal_response := "na"]

nameability_dt = nameability_dt%>%arrange(stimulus)


```

# Check if there are no batch discrepancies
```{r check if there are no batch discrepencies in h-index}

batch_nameability_dt = left_join(stimulus_by_h_index, stimulus_mode)

mean_h_batch1 = batch_nameability_dt[batch == "1", .(avg_h = mean(h_index_sum), sd_h = sd(h_index_sum))]

mean_h_rest = batch_nameability_dt[batch != "1", .(avg_h = mean(h_index_sum), sd_h = sd(h_index_sum))]

hist(batch_nameability_dt[batch == "1"]$h_index_sum)

hist(batch_nameability_dt[batch != "1"]$h_index_sum)

```

# Spell check
```{r}

unique_responses$lower_response <- as.character(unique_responses$lower_response)

unique_responses = unique_responses%>%arrange(stimulusitem2)

spellcheck <- hunspell(unique_responses$lower_response)

unique_responses$hunspell <- spellcheck

unique_responses$hunspell <- as.character(unique_responses$hunspell)

unique_responses[, suggested := hunspell_suggest(hunspell)]

unique_responses$suggested <- as.character(unique_responses$suggested)

unique_responses[suggested == "character", suggested := ""]

unique_responses[suggested == "", corrected_response := lower_response]

unique_responses$corrected_response <- trimws(unique_responses$corrected_response)

write_csv(unique_responses, "checkforspelling.csv")
```

# Reupload after RAs have checked for spelling - NEED TO DO

```{r}
library(readxl)
Tia <- tbl_dt(read_excel("checkforspelling_RA_Tia.xlsx"))
Stella <- tbl_dt(read_excel("checkforspelling_RA_Stella.xlsx"))

Tia$`Tia Kant` <- trimws(Tia$`Tia Kant`)
Stella$`Stella Mo` <- trimws(Stella$`Stella Mo`)

RA_naming = left_join(Tia, unique_responses)
RA_naming = left_join(RA_naming, Stella)

RA_naming[is.na(`Tia Kant`),  `Tia Kant`:= ""] 
RA_naming[is.na(`Stella Mo`),  `Stella Mo`:= ""] 

RA_naming[`Tia Kant` == `Stella Mo`, RA_match := 1]
RA_naming[`Tia Kant` != `Stella Mo`, RA_match := 0]



mean(RA_naming$RA_match)

RA_naming = RA_naming %>% arrange(RA_match)

write.csv(RA_naming, "RA_naming.csv")

```

```{r reupload verified responses}

verified_naming = read_csv("RA_naming_final.csv")

#join with original dataset
naming_with_final = left_join(data_clean, verified_naming)

naming = naming_with_final[, .(final, participant, latency, batch), by = stimulusitem2]

naming = naming[, stimulus_presentations := .N, by = stimulusitem2]

naming_unique = naming[, .(unique(c(final)), .N), by = .(stimulusitem2, final, stimulus_presentations, batch)]%>%arrange(stimulusitem2)

#calculate h-index

naming_unique[, proportion_response := N/stimulus_presentations]

naming_unique[, h_index := proportion_response*log2(1/proportion_response)]

naming_unique[, h_index_sum := sum(h_index), by = stimulusitem2]

stimulus_by_h_index_final = naming_unique[, .(unique(stimulusitem2)), by = h_index_sum]%>%arrange(desc(h_index_sum))

names(stimulus_by_h_index_final)[2] = "stimulusitem2"

#create a table with h-index and modal response

naming_unique = naming_unique%>%arrange(desc(N))

stimulus_mode_final = naming_unique[, .SD[1], by = stimulusitem2 ]

nameability_dt = left_join(stimulus_by_h_index_final, stimulus_mode_final)

nameability_dt = nameability_dt[, .(stimulusitem2, h_index_sum, final, proportion_response)]

names(nameability_dt)
names(nameability_dt)[1] = "stimulus"
names(nameability_dt)[2] = "h_index"
names(nameability_dt)[3] = "modal_response"

nameability_dt[is.na(modal_response) , modal_response := "na"]

nameability_dt = nameability_dt%>%arrange(stimulus)

```



# Unique modal names

```{r create a uniqueness pass fail}

unique_words = nameability_dt[, .N, by=.(modal_response)]
unique_words$modal_response = as.character(unique_words$modal_response)
nonunique_list = unique_words[N > 1,]$modal_response

nameability_dt[modal_response %in% nonunique_list, unique := 0]
nameability_dt[!modal_response %in% nonunique_list, unique := 1]

```


#scale the nameability
```{r scaled nameability}

nameability_dt[, scaled_name := 1 -percent_rank(h_index)] #1 is mst nameable, 0 is least nameable

```


# Export data to table

```{r}
write_csv(nameability_dt, "nameability_dt.csv")
```


# Create full table

```{r}

memorability_dt = read_csv("memorability_dt.csv")
orientation_dt = read_csv("orientation_dt.csv")

full_dt_pf = left_join(memorability_dt, orientation_dt)
full_dt_pf = left_join(full_dt_pf, nameability_dt)

write_csv(full_dt_pf, "full_dt_pf.csv")
```


# Demographics information

```{r}

demo_full = data_full[blockcode == 'demographics_block']
demo_full = demo_full[trialcode != 'raceother'] # there were two, which interfered with pivot tables
demo_full$response = as.character(demo_full$response)

demo_full1 = demo_full %>%
  group_by(participant, trialcode, date) %>%
  select(participant, trialcode, response) %>%
  pivot_wider(names_from = trialcode, values_from = response, values_fill = NA) %>%
  mutate(gender = as.character(gender),
         age = as.numeric(age))

# 2 people with overlapping participant ids (20, 21); seemed to have the same mturk id, so removed the second time (both did an experiment on date 52719, so removed that date)

demo_full1 = demo_full1[!demo_full1$participant %in% c(20, 21) | !demo_full1$date == 52719,]

# 1 person responded with 'b' to age/gender/education --> treat as non-response
# 1 non-response

demo1[demo1$age == '',]$age = '0'

demo_full2 = demo_full1 %>%
  mutate(gender = tolower(substr(gender,1,1))) %>%
  mutate(gender = case_when(gender == 'n' ~ 'n',
                            gender %in% c('f','w') ~ 'f',
                            gender == 'm' ~ 'm',
                            !gender %in% c('f','m','w', 'n') ~ '.'),
         age = as.numeric(as.character(age)))

# number of participants
nrow(demo_full2) # n=251

# gender, in percentages
table(demo_full2$gender)/(nrow(demo_full2))*100

# age (note that there is n=249 for age)
mean(demo_full2$age, na.rm=T) # 38.3
sd(demo_full2$age, na.rm=T) # 11.1
range(demo_full2$age, na.rm=T) # 19-73
hist(demo_full2$age)

```


```{r For cleaned data}

demo = data_full[blockcode == 'demographics_block' & participant %in% data_clean$participant]
demo = demo[trialcode != 'raceother'] # there were two, which interfered with pivot tables
demo$response = as.character(demo$response)

demo1 = demo %>%
  group_by(participant, trialcode, date) %>%
  select(participant, trialcode, response) %>%
  pivot_wider(names_from = trialcode, values_from = response, values_fill = NA) %>%
  mutate(gender = as.character(gender),
         age = as.numeric(age))

# 2 people with overlapping participant ids (20, 21); seemed to have the same mturk id, so removed the second time (both did an experiment on date 52719, so removed that date)
demo1 = demo1[!demo1$participant %in% c(20, 21) | !demo1$date == 52719,]

# 1 person responded with 'b' to age/gender/education --> treat as non-response
# 1 non-response

demo1[demo1$age == '',]$age = '0'

demo2 = demo1 %>%
  mutate(gender = tolower(substr(gender,1,1))) %>%
  mutate(gender = case_when(gender == 'n' ~ 'n',
                            gender %in% c('f','w') ~ 'f',
                            gender == 'm' ~ 'm',
                            !gender %in% c('f','m','w', 'n') ~ '.'),
         age = as.numeric(as.character(age)))

# number of participants
nrow(demo2) # n=251

# gender, in percentages
table(demo2$gender)/(nrow(demo2))*100

# age (note that there is n=249 for age)
mean(demo2$age, na.rm=T) # 38.3
sd(demo2$age, na.rm=T) # 11.1
range(demo2$age, na.rm=T) # 19-73
hist(demo2$age)

```

